Revisiting the von Bertalanffy Seasonal Cessational Growth Function of Pauly et al. (1992)

### 2016-04-15 manuscript_v0.Rmd
Starting to describe simulations in the ms

---
title: "Testing new Pauly Cessational Growth Function"
author: "Derek H. Ogle"
date: "April 9, 2016"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
  html_document:
    fig_height: 3.5
    fig_width: 4.5
csl: american-fisheries-society.csl
bibliography: SeasonalGrowth.bib
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(34738423)  # for reproducibility
library(FSA)
library(FSAsim)

@@

```{r maketprFun, echo=FALSE}
################################################################################
## internal function to compute t-prime
################################################################################
iCalc_tpr <- function(t,WP,NGT) {
  ## No-growth period starts at WP-NGT/2.  Use this to shift each age such that
  ##    first NGT would correspond to a value of 0
  tshift <- WP-NGT/2
  tmp.t <- t-tshift
  ## Find fraction of year on this new time scale for each adjusted age
  ##    by substracting whole number age (e.g, 2.79-2)
  tmp.t2 <- tmp.t-floor(tmp.t)
  ## Adjust this fraction for no growth ... with the time adjustment no-growth
  ##    is from 0 to NGT in each "year" ... tprime will not increase in NGT so
  ##    replace all of these fractions with zeroes.  Above NGT, the tprime must
  ##    have the NGT removed from it (e.g., if NGT=0.4, then 0.79-0.4 is the
  ##    fraction of the year for which growth occurred.)
  for (i in 1:length(tmp.t2)) {
    if (tmp.t2[i]<=NGT) tmp.t2[i] <- 0
    else tmp.t2[i] <- tmp.t2[i]-NGT
  }
  ## Now get the number of completed growth periods (i.e., floor (tmp.t)) times
  ##    the length of a growth period (1-NGT) to get the total growth periods
  ##    completed prior to that year and then add on the fractional piece
  tmp.t <- floor(tmp.t)*(1-NGT)+tmp.t2
  ## Shift back to get tprime (why is NGT needed here)
  tpr <- tmp.t+tshift+NGT
}
```

```{r makePaulyFun, echo=FALSE}
################################################################################
## Main Function
##   Linf, t0 as usual
##   Kpr = K-prime as defined in Pauly et al. (units are diff than usual K)
##   WP = "Winter Period" (middle point of no-growth period)
##      = ts+0.5 (ts from Pauly et al.)
##   NGT = "No Growth Time" = "fraction of a year where no growth occurs"
##   tpr = "t-prime" = actual age (t) minus cumulative NGT prior to t
################################################################################

paulySC <- function(t,Linf,Kpr=NULL,t0=NULL,WP=NULL,NGT=NULL) {
  if (length(Linf)==5) { Kpr <- Linf[[2]]; t0 <- Linf[[3]]
                         WP <- Linf[[4]]; NGT <- Linf[[5]]
                         Linf <- Linf[[1]] }
  tpr <- iCalc_tpr(t,WP,NGT)
  q <- Kpr*(tpr-t0) +
    (Kpr*(1-NGT)/(2*pi))*sin((2*pi)/(1-NGT)*(tpr-WP-0.5)) -
    (Kpr*(1-NGT)/(2*pi))*sin((2*pi)/(1-NGT)*(t0-WP-0.5))
  Linf*(1-exp(-q))
}
```

@@

\noindent where $NGT$ is the "no-growth time" or the length of the no growth period (as a fraction of a year) and $t^{'}$ is found by "subtracting from the real age ($t$) the total no-growth time occurring up to age $t$."  Furthermore,  @Paulyetal1992 introduced $K^{'}$ to `r eqncaps("PaulyMod",display="cite")` because the units of $K$ change from $year^{-1}$ in `r eqncaps("SomersMod",display="cite")` to $(1-NGT)^{-1}$ in `r eqncaps("PaulyMod",display="cite")` due to $t^{'}$&lt;$t$ for any $t$.  We further note that $K^{'}$&gt;$K$ because annual growth is compressed into a shorter period ($1-NGT$) in `r eqncaps("PaulyMod",display="cite")` when $NGT$&gt;0.

@Paulyetal1992 derived  `r eqncaps("PaulyMod",display="cite")` by assuming $C$=1 (i.e., that the rate of growth is 0 at the $WP$), replacing $2\pi$ with $\frac{2\pi}{1-NGT}$ (i.e., restricting the oscillation to the period of growth), and replacing $K$ with $K^{'}$.  Their modification can be described geometrically (though not algorithmically) in two steps.  First, the seasonal growth function in `r eqncaps("SomersMod",display="cite")` with $C$=1 is fit to the observed lengths and ages that have had the cumulative $NGT$ subtracted (i.e., using $t^{'}$).  The growth trajectory is then separated at the $WP$ and a horizontal segment that is $NGT$ units long is inserted.  This forms a growth trajectory that smoothly transitions into and out of a no-growth period (`r figcaps("PaulyExPlot",display="cite")`).

@@

```{r echo=FALSE, results="hide"}
## Setup
par(xaxs="i",yaxs="i",mar=c(3,3,0.6,0.6),mgp=c(1.7,.5,0),tcl=-0.3,las=1)
WP <- 0.55; NGT <- 0.3
Linf <- 30; Kpr <- 0.4; t0 <- -0.1
Pcf <- c(Linf,Kpr,t0,WP,NGT)
## Get growth trajectory
t <- seq(-0.1,3.3,length.out=499)
PL <- paulySC(t,Linf=Pcf)
## Make schematic plot
plot(c(-1,-1),xlim=c(-0.1,3.5),ylim=c(0,22),xaxt="n",
     ylab="Length",xlab="Age (years)")
axis(1,0:3)
## Put on NGT polygons
# find WPs and Lengths at WPs
WPs <- 0:2+WP
LatWPs <- paulySC(WPs,Linf=Pcf)
# find start and end of NGT
NGTs <- WPs-NGT/2
NGTe <- WPs+NGT/2
# place polygons
for (i in 1:length(NGTs)) polygon(c(NGTs[i],NGTs[i],NGTe[i],NGTe[i]),c(0,22,22,0),
                                  col=col2rgbt("black",1/20),border=NA)
## Put on the growth trajectory
lines(PL~t,lwd=2)
## Place an open point at the WP
points(WPs,LatWPs,pch=3,col="gray50")
## Add some important values to the age axis
axis(1,NGTs,tcl=-0.2)
axis(1,NGTe,tcl=-0.2)
## Add the t-prime labels
axis(1,at=c(0:3,NGTs,NGTe),labels=NA,tcl=0.2)
axis(1,at=0:3,labels=c(NA,0.7,1.4,2.1),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=NGTs,labels=c(0.4,1.1,1.8),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=NGTe,labels=c(0.4,1.1,1.8),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=3.3,labels="<= t",tick=FALSE)
axis(1,at=3.3,labels="<= t'",tick=FALSE,line=-1.7,lwd=0)

@@

@Paulyetal1992 provided a "diskette" that contained a computer program to estimate the parameters of `r eqncaps("PaulyMod",display="cite")`.  The diskette is difficult (at best) to obtain and the source code is no longer available (D. Pauly, pers. comm.).  @Paulyetal1992 did describe the operations performed by their program, but their is no description of how $t^{'}$ was operationalized.  This is an important step in using `r eqncaps("PaulyMod",display="cite")` because $t^{'}$ is a function of $t$, but it is also a function of $NGT$ and $t_{s}$, which are parameters to be estimated during the model-fitting process.  In other words, the values for $t^{'}$ will change with each iteration in the non-linear model-fitting process.

The objectives of this note are to (i) describe a function for calculating $t^{'}$ that may be used in the model-fitting process; (ii) describe a slight modification of `r eqncaps("PaulyMod",display="cite")` that eases the calculation of $t^{'}$ while providing a more meaningful parameter; (iii) provide an (open-source) algorithm for the modified function that can be used in model-fitting; and (iv) demonstrate the use of the modified function for fitting length-at-age data.

@@

The $WP$ value is equal to $t_{s}+0.5$ because of the shape of the sin function used to model the growth oscillations.  By simple substitution, `r eqncaps("PaulyMod",display="cite")` is modified to include $WP$ rather than $t_{s}$.

@@

$$
\begin{aligned}
q & =K^{'}(t^{'}-t_{0}) \\
  & +\frac{K^{'}(1-NGT)}{2\pi}sin\left(\frac{2\pi}{1-NGT}(t^{'}-WP-0.5)\right)  \quad \quad \quad \quad \text{`r paste0("(",eqncaps("PaulyMod2",display="num"),")")`} \\
  & -\frac{K^{'}(1-NGT)}{2\pi}sin\left(\frac{2\pi}{1-NGT}(t_{0}-WP-0.5)\right)
\end{aligned}  
$$

@@

Note that in `r eqncaps("PaulyMod2",display="cite")` $WP$ is the center of the no-growth period (`r figcaps("PaulyEx",display="cite")`).

# Methods
## Simulated Data

```{r echo=FALSE}
WP <- 0.8
NGT <- 0.5
gper <- c(WP+NGT/2-1,WP-NGT/2)*365
## Set some growth parameters
Linf <- 30; K <- 0.3; t0 <- 0
## Actually generate the data (with little variability)
d1 <- vbDataGen(200,Linf=Linf,K=K,t0=t0,maxAge=5,SE=0.01,SD=0.01,paramCV=0.01,
                growth.per=gper,sample.per=c(1,365),lendigs=1)
```

## R Implementation

# Model Fitting
## Simulated Data

```{r echo=FALSE, message=FALSE}
lwrbnd <- c(Linf=0,K=0,t0=-Inf,WP=0,NGT=0)
uprbnd <- c(Linf=Inf,K=Inf,t0=Inf,WP=1,NGT=1)
## Try fitting the PaulySC model
sv <- list(Linf=32,K=0.32,t0=0,WP=0.8,NGT=0.1)
fitP1 <- nls(lenCap~paulySC(ageFracY,Linf,K,t0,WP,NGT),data=d1,
             start=sv,lower=lwrbnd,upper=uprbnd,algorithm="port",control=list(maxiter=100))
## Make a diagnostic plot
plot(lenCap~ageFracY,data=d1,pch=19,col=col2rgbt("black",1/5))
curve(paulySC(x,coef(fitP1)),from=1,to=6,col="red",lwd=3,add=TRUE)
cfs <- coef(fitP1)
WPs <- 1:5+cfs[["WP"]]
LatWPs <- paulySC(WPs,Linf=cfs)
segments(WPs,LatWPs-2,WPs,LatWPs+2,lty=3,lwd=2,col="red")
SNGTs <- WPs-cfs[["NGT"]]/2
ENGTs <- WPs+cfs[["NGT"]]/2
segments(SNGTs,LatWPs-1,SNGTs,LatWPs+1,lty=3,lwd=2,col="blue")
segments(ENGTs,LatWPs-1,ENGTs,LatWPs+1,lty=3,lwd=2,col="blue")
legend("topleft",paste(c("WP","NGT"),c(WP,NGT),sep="="),
       bty="n",inset=-0.02,text.col=c("red","blue"))

cbind(Est=coef(fitP1),confint(fitP1))
```
```{r echo=FALSE}
plot(lenCap~ageFracY,data=d1,pch=19,col=col2rgbt("black",1/5),xlim=c(1.7,1.9),ylim=c(13.425,13.43))
curve(paulySC(x,coef(fitP1)),from=1,to=6,col="red",lwd=3,add=TRUE,n=1001)
segments(WPs,LatWPs-2,WPs,LatWPs+2,lty=3,lwd=2,col="red")
segments(SNGTs,LatWPs-1,SNGTs,LatWPs+1,lty=3,lwd=2,col="blue")
segments(ENGTs,LatWPs-1,ENGTs,LatWPs+1,lty=3,lwd=2,col="blue")

```{r echo=FALSE, message=FALSE}
## Try fitting the Somers model
vbSO <- vbFuns("Somers2")
fitSO1 <- nls(lenCap~vbSO(ageFracY,Linf,K,t0,C,WP),data=d1,
               start=list(Linf=32,K=0.32,t0=0,C=0.8,WP=0.8),
               lower=c(Linf=0,K=0,t0=-Inf,C=-1,WP=0),
               upper=c(Linf=Inf,K=Inf,t0=Inf,C=2,WP=1),
               algorithm="port",control=list(maxiter=100),trace=FALSE)
plot(lenCap~ageFracY,data=d1,pch=19,col=col2rgbt("black",1/5))
curve(vbSO(x,coef(fitSO1)),from=1,to=6,col="red",lwd=2,add=TRUE)
cbind(coef(fitSO1),confint(fitSO1))
```

@@

## Appendix

```{r}
<<maketprFun>>
```

```{r}
<<makePaulyFun>>
```

## References

>>>>

---
title: "Revisiting the von Bertalanffy Seasonal Cessational Growth Function of Pauly et al. (1992)"
author: "Derek H. Ogle"
date: "April 9, 2016"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
  html_document:
    fig_height: 3.5
    fig_width: 4.5
csl: american-fisheries-society.csl
bibliography: SeasonalGrowth.bib
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(34738423)  # for reproducibility
library(FSA)
library(FSAsim)
library(knitr)

source("iCalc_tpr.R")
source("VBSCGF.R")

@@

@@

\noindent where $NGT$ is the "no-growth time" or the length of the no growth period (as a fraction of a year) and $t^{'}$ is found by "subtracting from the real age ($t$) the total no-growth time occurring up to age $t$."  Furthermore,  @Paulyetal1992 noted that the units on $K$ changed from $year^{-1}$ in `r eqncaps("SomersMod",display="cite")` to $(1-NGT)^{-1}$ in `r eqncaps("PaulyMod",display="cite")`.  To eliminate confusion he suggested using $K^{'}$ in `r eqncaps("PaulyMod",display="cite")`, as we do here.

@Paulyetal1992 derived  `r eqncaps("PaulyMod",display="cite")` by assuming $C$=1 (i.e., that the rate of growth is 0 at the $WP$) and replacing $2\pi$ with $\frac{2\pi}{1-NGT}$ (i.e., restricting the oscillation to the period of growth and noting that $K^{'}$ only operates in this shorter period).  Their modification can be described geometrically (though not algorithmically) in two steps.  First, the seasonal growth function in `r eqncaps("SomersMod",display="cite")` with $C$=1 is fit to the observed lengths and ages that have had the cumulative $NGT$ subtracted (i.e., using $t^{'}$).  The growth trajectory is then separated at the $WP$ and a horizontal segment that is $NGT$ units long is inserted.  This forms a growth trajectory that smoothly transitions into and out of a no-growth period (`r figcaps("PaulyExPlot",display="cite")`).

@@

```{r echo=FALSE, results="hide"}
## Setup
par(xaxs="i",yaxs="i",mar=c(3,3,0.6,0.6),mgp=c(1.7,.5,0),tcl=-0.3,las=1)
WP <- 0.55; NGT <- 0.3
Linf <- 30; K <- 0.3; Kpr <- K/(1-NGT); t0 <- 0
Pcf <- c(Linf,Kpr,t0,WP,NGT)
## Get growth trajectory
t <- seq(-0.1,3.3,length.out=499)
PL <- VBSCGF(t,Linf=Pcf)
## Calculate WPs and start and end of NGT
# find WPs and Lengths at WPs
WPs <- 0:2+WP
LatWPs <- VBSCGF(WPs,Linf=Pcf)
# find start and end of NGT
NGTs <- WPs-NGT/2
NGTe <- WPs+NGT/2
## Make schematic plot
plot(c(-1,-1),xlim=c(-0.1,3.5),ylim=c(0,22),xaxt="n",
     ylab="Length",xlab="Age (years)")
## Put on NGT polygons
for (i in 1:length(NGTs)) polygon(c(NGTs[i],NGTs[i],NGTe[i],NGTe[i]),c(0,22,22,0),
                                  col=col2rgbt("black",1/20),border=NA)
## Put on the growth trajectory
lines(PL~t,lwd=2)
## Place a point at the WP
points(WPs,LatWPs,pch=3,col="gray50")
## Add some important values to the age axis
axis(1,0:3)
axis(1,NGTs,tcl=-0.2)
axis(1,NGTe,tcl=-0.2)
## Add the t-prime labels
# makes inside ticks
axis(1,at=c(0:3,NGTs,NGTe),labels=NA,tcl=0.2)
axis(1,at=1:3,labels=iCalc_tpr(1:3,WP,NGT),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=NGTs,labels=iCalc_tpr(NGTs,WP,NGT),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=NGTe,labels=iCalc_tpr(NGTe,WP,NGT),tcl=0.2,line=-1.7,lwd=0)
axis(1,at=3.3,labels="<= t",tick=FALSE)
axis(1,at=3.3,labels="<= t'",tick=FALSE,line=-1.7,lwd=0)

@@

@Paulyetal1992 provided a "diskette" that contained a computer program to estimate the parameters of `r eqncaps("PaulyMod",display="cite")`.  The diskette is difficult (at best) to obtain and the source code is no longer available (D. Pauly, pers. comm.).  @Paulyetal1992 did describe the operations performed by their program, but there is no description of how $t^{'}$ was operationalized.  This is an important step in using `r eqncaps("PaulyMod",display="cite")` because $t^{'}$ is a function of $t$, but it is also a function of $NGT$ and $t_{s}$, which are parameters to be estimated during the model-fitting process.  In other words, the values for $t^{'}$ will change with each iteration in the non-linear model-fitting process.

Therefore, the objectives of this note are to (i) describe a function for calculating $t^{'}$ that may be used in the model-fitting process; (ii) describe a slight modification of `r eqncaps("PaulyMod",display="cite")` that eases the calculation of $t^{'}$ while providing a more meaningful parameter; (iii) provide an (open-source) algorithm for the modified function that can be used in model-fitting; and (iv) demonstrate the use of the modified function for fitting length-at-age data.

@@

In `r eqncaps("SomersMod",display="cite")`, $WP=t_{s}+\frac{1}{2}$ because the sine function has a period of one year.  The growth period is compressed in `r eqncaps("PaulyMod",display="cite")` to be $1-NGT$.  Thus, the start of the no-growth period ($SNG$) is $t_{s}+\frac{1-NGT}{2}$.  The center of the no-growth period is then $SNG+\frac{NGT}{2}$ or $t_{s}+\frac{1}{2}$.  Thus, $WP=t_{s}+\frac{1}{2}$ is the center of the no-growth period for `r eqncaps("PaulyMod",display="cite")`.

By simple substitution, `r eqncaps("PaulyMod",display="cite")` is modified to include $WP$ rather than $t_{s}$.

@@

$$
\begin{aligned}
q & =K^{'}(t^{'}-t_{0}) \\
  & +\frac{K^{'}(1-NGT)}{2\pi}sin\left(\frac{2\pi}{1-NGT}(t^{'}-WP-\frac{1}{2})\right)  \quad \quad \quad \quad \text{`r paste0("(",eqncaps("PaulyMod2",display="num"),")")`} \\
  & -\frac{K^{'}(1-NGT)}{2\pi}sin\left(\frac{2\pi}{1-NGT}(t_{0}-WP-\frac{1}{2})\right)
\end{aligned}  
$$

@@

As noted by @Paulyetal1992 the calculation of $t^{'}$ depends on the observed age ($t$) and the cumulative no-growth time prior to $t$.  In practice, the calculation of $t^{'}$ also depends on the position of the no-growth period within a year.  Here, the position of the no-growth period is defined by the $SNG$.  However, because the $SNG$ has a one-to-one relation with $WP$ and $t_{s}$ it can also be defined relative to these parameters.

The following algorithm is used to convert from observed ages ($t$) to ages adjusted for cumulative $NGT$ prior to age $t$ ($t^{'}$).

1. Shift the age ($t$) by subtracting the start of the no-growth period ($SNG$) from $t$, such that a whole number age represents the start of a no-growth period.  For example, if $SNG$=0.4, then $t$=2.4 will become 2.0 and $t$=2.9 will become 2.5.
1. Subtract the whole number age from the shifted age such that the remaining decimal represents the fraction of a shifted year.  For example, a 0 will result if the shifted age is 2.0 and a 0.5 will result if the shifted age is 2.5.
1. Substract the $NGT$ from each of the values from the previous step.
1. If the value from the previous step is negative, then the age is within the no-growth period and the negative value should be replaced with a zero.  Otherwise, the positive value represents the fraction of a growth period completed.
1. Add the value from the previous step to the total growth time completed (i.e., the product of the number of growth periods completed and the length of the growth period ($1-NGT$)).
1. Compute $t{'}$ by adding back the $SNG$ that was subtracted in Step 1.

Further examples of $t^{'}$ values relative to $t$ values are shown in `r figcaps("PaulyExPlot",display="cite")`.  This algorithm for computing $t^{'}$ is implemented in an R [@R2016] function as shown in Appendix 1.  With this, `r eqncaps("paulyMod2",display="cite")` is easly implemented as an R function as shown in Appendix 2.

# Fitting the Modified Model
## Simulated Data
Fish ages (including fractions of a year) and lengths at capture were simulated with vbDataGen() from the FSAsims package (CITATION) in R.  In this application, this functions simulates seasonal fish growth with the following steps: 
```{r echo=FALSE, results='hide'}
## Set some common parameters
Linf <- 30; K <- 0.3; t0 <- -0.1
## Set bounds for model-fitting
lwrbnd <- c(Linf=0,K=0,t0=-Inf,WP=0,NGT=0)
uprbnd <- c(Linf=Inf,K=Inf,t0=Inf,WP=1,NGT=1)
```

```{r echo=FALSE, results="hide", message=FALSE}
## Setup
par(xaxs="i",yaxs="i",mar=c(3,3,0.6,0.6),mgp=c(1.7,.5,0),tcl=-0.3,las=1)
## Set some specific growth parameters
# fairly typical north temperate situation
WP <- 0.8; NGT <- 0.5
gper <- c(WP+NGT/2-1,WP-NGT/2)*365
## Actually generate the data (with very little variability)
d1 <- vbDataGen(200,Linf=Linf,K=K,t0=t0,maxAge=5,SE=0.001,SD=0.001,paramCV=0.001,
                growth.per=gper,sample.per=c(1,365),lendigs=1)
## Try fitting the VBSCGF model
sv <- list(Linf=32,K=0.32,t0=0,WP=0.9,NGT=0.3)
fitP1 <- nls(lenCap~VBSCGF(ageFracY,Linf,K,t0,WP,NGT),data=d1,
             start=sv,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
( cfs <- coef(fitP1) )
## A plot
plot(lenCap~ageFracY,data=d1,pch=19,col=col2rgbt("black",1/3),
     xlab="Age (years)",ylab="Length",xlim=c(1,6),ylim=c(7,27))
curve(VBSCGF(x,coef(fitP1)),from=1,to=6,lwd=2,add=TRUE)
WPs <- 1:5+cfs[["WP"]]
LatWPs <- VBSCGF(WPs,Linf=cfs)
arrows(WPs,LatWPs+2,WPs,LatWPs+0.2,lwd=2,length=0.1)
SNGTs <- WPs-cfs[["NGT"]]/2
ENGTs <- WPs+cfs[["NGT"]]/2
arrows(SNGTs,LatWPs-0.7,ENGTs,LatWPs-0.7,lwd=2,length=0.05,angle=90,code=3)

tmp <- c("Linf=","K=","t0=","WP=","NGT=")
legend("topleft",paste0(c("Set Values",tmp),c("",Linf,K,t0,WP,NGT)),
       bty="n",inset=-0.02,cex=0.8)
cfs <- round(cbind(Est=coef(fitP1),confint(fitP1)),3)
legend("bottomright",c("Estimated Values",paste0(tmp,cfs[,1]," (",cfs[,2],",",cfs[,3],")")),bty="n",cex=0.8)
```

```{r echo=FALSE, results="hide", message=FALSE}
## Setup
par(xaxs="i",yaxs="i",mar=c(3,3,0.6,0.6),mgp=c(1.7,.5,0),tcl=-0.3,las=1)
## Set some specific growth parameters
# fairly typical north temperate situation
WP <- 0.8; NGT <- 0.5
gper <- c(WP+NGT/2-1,WP-NGT/2)*365
## Actually generate the data (with more variability)
d1 <- vbDataGen(200,Linf=Linf,K=K,t0=t0,maxAge=5,SE=0.2,SD=0.5,paramCV=0.01,
                growth.per=gper,sample.per=c(1,365),lendigs=1)
## Try fitting the VBSCGF model
sv <- list(Linf=32,K=0.32,t0=0,WP=0.9,NGT=0.3)
fitP1 <- nls(lenCap~VBSCGF(ageFracY,Linf,K,t0,WP,NGT),data=d1,
             start=sv,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
( cfs <- coef(fitP1) )
## A plot
plot(lenCap~ageFracY,data=d1,pch=19,col=col2rgbt("black",1/3),
     xlab="Age (years)",ylab="Length",xlim=c(1,6),ylim=c(7,27))
curve(VBSCGF(x,coef(fitP1)),from=1,to=6,lwd=2,add=TRUE)
WPs <- 1:5+cfs[["WP"]]
LatWPs <- VBSCGF(WPs,Linf=cfs)
arrows(WPs,LatWPs+2,WPs,LatWPs+0.2,lwd=2,length=0.1)
SNGTs <- WPs-cfs[["NGT"]]/2
ENGTs <- WPs+cfs[["NGT"]]/2
arrows(SNGTs,LatWPs-0.7,ENGTs,LatWPs-0.7,lwd=2,length=0.05,angle=90,code=3)

tmp <- c("Linf=","K=","t0=","WP=","NGT=")
legend("topleft",paste0(c("Set Values",tmp),c("",Linf,K,t0,WP,NGT)),
       bty="n",inset=-0.02,cex=0.8)
cfs <- round(cbind(Est=coef(fitP1),confint(fitP1)),3)
legend("bottomright",c("Estimated Values",paste0(tmp,cfs[,1]," (",cfs[,2],",",cfs[,3],")")),bty="n",cex=0.8)
```

```{r echo=FALSE, results="hide", message=FALSE}
## Setup
par(xaxs="i",yaxs="i",mar=c(3,3,0.6,0.6),mgp=c(1.7,.5,0),tcl=-0.3,las=1)
## Set some specific growth parameters
# fairly typical north temperate situation
WP <- 0.8; NGT <- 0.5
gper <- c(WP+NGT/2-1,WP-NGT/2)*365
## Actually generate the data (with more variability)
d1 <- vbDataGen(200,Linf=Linf,K=K,t0=t0,maxAge=5,SE=0.2,SD=0.5,paramCV=0.01,
                growth.per=gper,sample.per=c(1,365),lendigs=1)
## Try fitting the VBSCGF model
sv <- list(Linf=32,K=0.32,t0=0,WP=0.9,NGT=0.3)
fitP1 <- nls(lenCap~VBSCGF(ageFracY-0.3,Linf,K,t0,WP,NGT),data=d1,
             start=sv,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
( cfs <- coef(fitP1) )
## A plot
plot(lenCap~I(ageFracY-0.3),data=d1,pch=19,col=col2rgbt("black",1/3),
     xlab="Age (years)",ylab="Length",xlim=c(1,6),ylim=c(7,27))
curve(VBSCGF(x,coef(fitP1)),from=1,to=6,lwd=2,add=TRUE)
WPs <- 1:5+cfs[["WP"]]
LatWPs <- VBSCGF(WPs,Linf=cfs)
arrows(WPs,LatWPs+2,WPs,LatWPs+0.2,lwd=2,length=0.1)
SNGTs <- WPs-cfs[["NGT"]]/2
ENGTs <- WPs+cfs[["NGT"]]/2
arrows(SNGTs,LatWPs-0.7,ENGTs,LatWPs-0.7,lwd=2,length=0.05,angle=90,code=3)

tmp <- c("Linf=","K=","t0=","WP=","NGT=")
legend("topleft",paste0(c("Set Values",tmp),c("",Linf,K,t0,WP-0.3,NGT)),
       bty="n",inset=-0.02,cex=0.8)
cfs <- round(cbind(Est=coef(fitP1),confint(fitP1)),3)
legend("bottomright",c("Estimated Values",paste0(tmp,cfs[,1]," (",cfs[,2],",",cfs[,3],")")),bty="n",cex=0.8)
```

@@

# Discussion

# Appendices
## Appendix 1

```{r echo=FALSE, comment=""}
cat(readLines("iCalc_tpr.R"),sep="\n")
```

## Appendix 2

```{r echo=FALSE, comment=""}
cat(readLines("VBSCGF.R"),sep="\n")
```

# References
